%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Irabiel Romero} \\ \vspace{1pt}
    \small 661-240-7760 $|$ \href{mailto:x@x.com}{\underline{Irabiel.Romero@student.csulb.edu}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/irabiel}} $|$
    \href{https://github.com/...}{\underline{github.com/irabiel}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California State University Long Beach }{Long Beach, CA}
      {M.S. in Applied Mathematics	}{Aug. 2018 -- May 2021}
        \resumeItemListStart
            \resumeItem{Thesis: Numerical Methods for Multiscale Modeling in Bacterial Colony Growth}
            \resumeItem{Adviser: Dr. Hui Sun }
        \resumeItemListEnd
    \resumeSubheading
      {California State University Long Beach }{Long Beach, CA}
      {B.S. in Applied Mathematics 	}{Aug. 2016 -- May 2018}
      \resumeSubheading
      {California State University Long Beach}{Long Beach, CA}
      {B.A. in Physics 	}{Aug. 2016 -- May 2018}
      \resumeSubheading
      {Bakersfield College 	}{Bakersfield, CA}
      {A.S in Mathematics}{Sept. 2013 -- May 2016}
  \resumeSubHeadingListEnd

%-----------MANUSCRIPT-----------
\section{Manuscript}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Under preparation}{}
      {University of California San Diego}{San Diego}
      \resumeItemListStart
        \resumeItem{Title:}
            \resumeItemListStart
                \resumeItem{A multigrid method on stiff reaction-diffusion systems for bacterial colony development.}
            \resumeItemListEnd
        \resumeItem{Authorship:}
            \resumeItemListStart
                \resumeItem{Hui Sun, Irabiel Romero, and Bo Li}
            \resumeItemListEnd
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Teaching Assistant}{Aug. 2020 -- Present}
      {California State University Long Beach}{ Long Beach}
      \resumeItemListStart
        \resumeItem{Teach four sections of Precalculus}
        \resumeItem{Hold office hours for students and Grade exams}
      \resumeItemListEnd
    \resumeSubheading
      {Research Assistant}{June 2018 -- Present}
      {California State University Long Beach}{ Long Beach}
      \resumeItemListStart
        \resumeItem{Aug. 2020 -- Present}
       \resumeItemListStart
        \resumeItem{Help implement n-dimensional Newton-Multigrid for a 2D system of one nonlinear of PDE and system of two coupled nonlinear of PDEs}
        \resumeItem{Integrated Newton-Multigrid to already existing kinetic Monte Carlo model}
        \resumeItemListEnd
        \resumeItem{June 2019 -- Aug. 2019}
       \resumeItemListStart
        \resumeItem{Help implement n-dimensional Modified Newton for a 1D system of three nonlinear PDEs}
        \resumeItem{Integrated n-dimensional Modified Newton method and Multigrid method}
        \resumeItemListEnd
        \resumeItem{June 2018 -- Aug. 2018}
       \resumeItemListStart
        \resumeItem{Modified the Bacterial Colony Mathematical Model, containing only Carbon, to include Oxygen and Acetate}
        \resumeItem{Create a 1D model to simulate nutrient profile down the center of the colony}
        \resumeItemListEnd
    \resumeItemListEnd

    \resumeSubheading
      {Graduate Assistant}{Aug. 2018 -- Present}
      {California State University Long Beach}{ Long Beach}
      \resumeItemListStart
        \resumeItem{Grade quizzes, re-quizzes, exams, and re-exams}
        \resumeItem{Hold office hours for students}
        \resumeItem{Monitor computer lab and provide basic technical assistance to students}
      \resumeItemListEnd
      
      \resumeSubheading
      {Lindgren Math Tutorial Center Tutor}{Sept. 2017 -- May 2020}
      {California State University Long Beach}{ Long Beach}
      \resumeItemListStart
        \resumeItem{Helped students increase their confidence in a particular subject matter as well as in their academic skills}
        \resumeItem{Specialized in calculus-based courses (i.e., Ordinary Differential Equations I/II, Partial Differential Equations, Numerical Analysis, etc.)}
      \resumeItemListEnd
      
      \resumeSubheading
      {Bickerstaff Academic Center for Athletes}{Feb. 2017 – Aug. 2018 }
      {California State University Long Beach}{ Long Beach}
      \resumeItemListStart
        \resumeItem{Specialized mathematics content tutoring on a one to one basis}
        \resumeItem{Helped students refine learning skills such as note-taking, test preparation, and problem-solving}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------Research Projects-----------
\section{Research Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Modeling Pedestrian Movements using Stochastic Differential Equations }{}
      {under Dr. Chung-min Lee}{}
      \resumeItemListStart
        \resumeItem{Modeling individual pedestrian movements on the first floor of the CSULB Liberal Arts 5 building}
        \resumeItem{Approximated system of Stochastic Differential Equations using the Euler-Maruyama method}
        \resumeItem{In charge of overseeing the project and lead programmer}
        \resumeItem{Implemented algorithms using MATLAB}
      \resumeItemListEnd
      
      \resumeSubheading
      {Find Shortest Path of a graph modeling the city of Oldenburg Germany }{}
      {under Dr. Lee}{}
      \resumeItemListStart
        \resumeItem{Dataset Road Network data from the University of Utah}
        \resumeItem{Use contraction to simplify the graph}
        \resumeItem{Find the shortest path of the simplified graph}
        \resumeItem{Then find the shortest path of the subgraphs in the shortest path of the simplified graph}
        \resumeItem{Implemented algorithms using MATLAB}
      \resumeItemListEnd
      
      \resumeSubheading
      {Pedestrian Crowd Density Simulations using Finite Element Method }{}
      {under Dr. Lee}{}
      \resumeItemListStart
        \resumeItem{Approximating first-order nonlinear nonlocal conservation law for non-Newtonian fluid}
        \resumeItem{Approximating two systems of Eikonal equation for desired crowd velocity and obstacle avoidance}
        \resumeItem{Analyzing pedestrian crowd density within a closed environment}
        \resumeItem{Implemented algorithms using MATLAB}
      \resumeItemListEnd
      
      \resumeSubheading
      {Approximating solutions for Reaction-Diffusion Partial Differential Equations }{}
      {under Dr. Hui Sun}{}
      \resumeItemListStart
        \resumeItem{Applications in Biology regarding the colony growth of E Coli}
        \resumeItem{Analyzing the Reaction-Diffusion model}
        \resumeItem{Implemented algorithms using MATLAB}
      \resumeItemListEnd
      
      \resumeSubheading
      {1-Dimensional simulation of the nutrient profile of bacterial colony}{}
      {under Dr. Sun}{}
      \resumeItemListStart
        \resumeItem{Model the nutrient profile of the center of a bacterial colony}
        \resumeItem{Implemented algorithms using MATLAB}
      \resumeItemListEnd
      
      \resumeSubheading
      {Create a linear solver to solve nonlinear PDEs }{}
      {under Dr. Sun}{}
      \resumeItemListStart
        \resumeItem{Integrated n-dimensional Modified Newtons method and Multigrid method to solve a system on nonlinear PDEs}
        \resumeItem{Implemented algorithms using MATLAB}
      \resumeItemListEnd
      
      \resumeSubheading
      {Integrating discrete 2D lattice kinetic Monte Carlo model and continuous Newton-Multigrid method }{}
      {under Dr. Sun}{}
      \resumeItemListStart
        \resumeItem{Create 2D Newton-Multigrid for a coupled system of PDEs for the nutrient profile}
        \resumeItem{In charge of overseeing the project and lead programmer}
        \resumeItem{Implemented algorithms using C++}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------FELLOWSHIPS, HONORS, AND AWARDS-----------
\section{Fellowships, Honors, and Awards}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Dean's List}}{Fall 2017}
      \resumeProjectHeading
          {\textbf{President’s List}}{Spring 2018}
     \resumeProjectHeading
          {\textbf{Samuel Councilman Scholarship}}{Fall 2019}
      \resumeProjectHeading
          {\textbf{Richard Green Grad Fellowship}}{Fall 2020}
    \resumeSubHeadingListEnd

%-----------ORAL PRESENTATIONS-----------
\section{Oral Presentations}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{31st Annual CSULB Student Research Competition }}{Spring 2019}
          \resumeItemListStart
            \resumeItem{Spatiotemporal Establishment of Growing Bacterial Colonies}
      \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{32nd Annual CSULB Student Research Competition }}{Spring 2020}
          \resumeItemListStart
            \resumeItem{Numerical Methods for Multiscale Modeling in Bacterial Colony Growth}
      \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{SIAM Conference on the Life Sciences}}{Summer 2020}
          \resumeItemListStart
            \resumeItem{Development of Newton-Multigrid for Multiscale Modeling in Bacterial Colony Growth}
            \resumeItem{Canceled due to Covid-19}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Poster PRESENTATIONS-----------
\section{Poster Presentations}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Graduate Research Conference}}{Fall 2018}
          \resumeItemListStart
            \resumeItem{Spatiotemporal Establishment of Growing Bacterial Colonies}
      \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Graduate Research Conference }}{Fall 2019}
          \resumeItemListStart
            \resumeItem{Numerical Methods for Multiscale Modeling in Bacterial Colony Growth}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------COMPUTER AND COMPUTATIONAL SKILLS-----------
\section{Computer and Computational Skills}
    \resumeSubHeadingListStart
      \resumeItemListStart
      \resumeItem{Create approximations for integrals using various methods}
      \resumeItem{Create approximations for solving PDEs and ODEs using Finite Difference and Finite Elements Method}
      \resumeItem{Create approximations for solving SDEs using Euler-Maruyama method}
      \resumeItem{Solve Matrix systems with various methods}
      \resumeItem{Optimization algorithms from Gradient Descent, Newton's method, and Particle Swarm Optimization}
      \resumeItem{Machine learning Algorithms using TensorFlow, and PyTorch in Python}
      \resumeItem{Comfortable with Linux, Macs, and Windows operating systems}
      \resumeItem{Comfortable with GitHub}
      \resumeItem{Comfortable using terminal}
      \resumeItem{Proficient in MATLAB}
      \resumeItem{Proficient in Python}
      \resumeItem{Proficient in C++}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------OTHER SKILLS-----------
\section{Other Skills}
    \resumeSubHeadingListStart
      \resumeItemListStart
        \resumeItem{Spanish}
      \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------REFERENCES -----------
\section{References}
    \resumeSubHeadingListStart
      \resumeItemListStart
      \resumeItem{Dr. Hui Sun, Ph.D.: Paul.Sun@csulb.edu}
      \resumeItem{Dr. Chung-min Lee, Ph.D.: Chung-min.Lee@csulb.edu}
      \resumeItem{Dr. Bruce Chaderjain, Ph.D.: Bruce.Chaderjian@csulb.edu }
      \resumeItem{Dr. Eun Heui Kim, Ph.D.: Eunheui.Kim@csulb.edu}
      \resumeItem{Dr. Tangan Gao, Ph.D.: Tangan.Gao@csulb.edu }
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
